---
title       : Traffic Classification
subtitle    : Research into the Area of Security
author      : Yinsen Miao
job         : Master in Statistics
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
logo        : Rice-University.png
hitheme     : tomorrow      # 
widgets     : [mathjax, quiz, bootstrap]            # 
ext_widgets: {rCharts: [libraries/nvd3]}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Dataset

| Name     | Year 	| Dimension 	| Labeled 	| Raw  	| Description 	|
|:---------------------------------------------------------------------:	|-----------	|:---------:	|:-------:	|:-------:	|--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------	|
| [WIDE](http://mawi.wide.ad.jp/mawi/) 	| 2006-2014 	| >>1B 	| No 	| Yes 	| Daily 15-minute traffic trace collected by US-JP backbone network and has been [anonymized](http://mawi.wide.ad.jp/mawi/guideline.txt) by deleting payload. But might be useful.   	|
| [CAIDA](http://www.caida.org/data/overview/) 	| 2008-2014 	| >>1B 	| No 	| Yes 	| Monthly anonymized traffic traces from the "equinix-chicago" and "equinix-sanjose" high-speed monitors. But might be useful for unsupervised learning. 	|
| [WITS](http://wand.net.nz/wits/) 	| 2002-2010 	| >>1B 	| No 	| Yes 	| Cannot be downloaded via IPv4 network. 	|
| [LBNL/ICSI](http://www.icir.org/enterprise-tracing/download.html) 	| 2004 	| >>10K 	| No 	| Yes 	| Anonymized traffic traces 	|
| [UPC-CCABA](http://loadshedding.ccaba.upc.edu/traffic_classification) 	| 2013 	| >1B 	| Yes 	| Unknown 	| 535K of the flows are labeled. The dataset is already requested pending to download. 	|
| [UNIBS](http://www.ing.unibs.it/ntw/tools/traces/) 	| 2009 	| 78K 	| Yes 	| Yes 	| Traffic collected from a subnet of 20 hosts used by students and dept. personnel, anonymized but with associated ground truth metadata, collected with the [GT tool](http://www.ing.unibs.it/ntw/tools/gt/). 	|


--- #id1
## Resource Paper
[A summary of papers (1994-2009) from CAIDA](http://www.caida.org/research/traffic-analysis/classification-overview/)

--- #id2

## OMP performance (Accuracy)
```{r setoptions,echo=FALSE}
    opts_chunk$set(cache = T)
```

```{r,echo=FALSE}
library(plyr)
library(ggplot2)
load("./rlist.RData")

p <- rep(c(.01, .1, .2, .4, .8, .99), each = 16)
iter <- rep(c(1, 2, 5, 10, 15, 20, 25, 50), 12)

tr.acc <- sapply(rlist, function(i) sum(diag(i$train)) / sum(i$train))
tt.acc <- sapply(rlist, function(i) sum(diag(i$test)) / sum(i$test))    
time <- sapply(rlist, function(i) i$time)

all.tr <- data.frame(p = p * 100, iter = iter, acc = tr.acc, type = "train")
all.tt <- data.frame(p = p * 100, iter = iter, acc = tt.acc, type = "test")
all.time <- data.frame(p = p * 100, iter = iter, time = time)
all.res <- rbind(all.tr, all.tt)
all.res$iter <- as.factor(all.res$iter)


all.p <- ddply(all.res, .(p, iter, type), summarize, sd = sd(acc), mean = mean(acc), se = sd(acc)/sqrt(length(acc)), count = length(acc))
all.time.p <- ddply(all.time, .(p, iter), summarize, sd = sd(time), mean = mean(time), se = sd(time) / sqrt(length(time)), count = length(time))

```

```{r,echo=FALSE,fig.align='center',fig.height=10,fig.width=20}
ggplot(all.p, aes(x = p, y = mean, colour = type, label = round(mean,2))) + 
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 1, lwd = 0.7) +
    geom_line(lwd = 0.7) +
    geom_point(size = 2) +
    geom_text(size = 4, color = "black", hjust = 1) +
    facet_wrap(~ iter, nrow = 2) +
    theme_bw() +
    ggtitle("Training Size versus Overall Accuarcy (249 features)") + 
    xlab("Pecentage %") + ylab("Overall Accuracy")
```

---

## OMP performance (Time comsumption)
```{r,echo=FALSE,fig.align='center',fig.height=10,fig.width=20}
ggplot(all.time.p, aes(x = p, y = mean, color = "red", label = round(mean,2))) + 
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 3, lwd = 0.7) +
    geom_line(lwd = 0.7) +
    geom_point(size = 2) +
    geom_text(size = 4, color = "black", hjust = 1) +
    facet_wrap(~ iter, nrow = 2) +
    coord_cartesian(xlim = c(-20, 120)) +
    theme_bw() + theme(legend.position="none") +
    ggtitle("Average Testing Time (249 features)") + 
    xlab("Pecentage %") +  
    ylab("Time in Second")
```

---

## Paper about on-line learning
[On-line SVM traffic classification](https://www.dropbox.com/s/e4vfp6mamaca3ri/2011-On-line%20SVM%20traffic%20classification.pdf)
>
* Parallelized optimized SVM on [CoMo](http://como.sourceforge.net/index.php) platform.
* C source code implemented in SVM, Naived Bayes [available](http://www.ing.unibs.it/ntw/tools/como-modules/)
* Dataset used [UNIBS (labeled)](http://www.ing.unibs.it/ntw/tools/traces/), [AUCK](http://wand.net.nz/wits/), [MAWI](http://mawi.wide.ad.jp/mawi/), [CAIDA](http://www.caida.org/data/overview/).
* Mainly talked about CPU time and memory comsumption but didn't mention their accuracy performance or even how they manage to train their supervised SVM on unlabeled dataset.  

[MTCLASS: Traffic Classification on High-Speed Links with Commodity Hardware]()

---




